SVG: The Paper

### 2022-04-14 Analysis/index.Rmd
2nd and 3rd place candidates

```{r, echo = TRUE}
n_breaks = 25

a %>% mutate(b_bin = cut(max_b, breaks = n_breaks, labels = FALSE)) %>%
  group_by(condition, b_bin) %>% 
  summarise(acc = mean(selected_max), .groups = "drop") %>%
  mutate(b_bin = as.numeric(b_bin)/n_breaks) -> a_cut
```

@@

We can also repeat this calculate for all other items during/in a trial - is our model accurate/calibrated in cases when 
the participant did not select the item with the highest model weight?

@@

>>>>

```{r, echo = TRUE}
my_breaks = seq(0.0, 1, 0.05)

a %>% mutate(b_bin = cut(max_b, breaks = my_breaks, labels = FALSE)) %>%
  group_by(condition, b_bin) %>% 
  summarise(acc = mean(selected_max), .groups = "drop") %>%
  mutate(b_bin = as.numeric(b_bin)/(length(my_breaks)-1)) -> a_cut
```

@@

We can also repeat this calculate for the 2nd and 3rd ranked candidate items.

```{r fig.cap = "This plot shows how often the 2nd and 3rd ranked items are selected based on the weights assigned by the model."}
a %>% select(max_b2, max_b3, selected_max2, selected_max3) %>%
  unite(`2`, max_b2, selected_max2) %>%
  unite(`3`, max_b3, selected_max3) %>%
  pivot_longer(c(`2`, `3`), names_to = "rank", values_to = "b") %>%
  separate(b, into = c("b", "selected"), sep = "_", convert = TRUE) %>%
  mutate(b_bin = cut(b, breaks = my_breaks, labels = FALSE)) %>%
  group_by(b_bin) %>% 
  summarise(acc = mean(selected), .groups = "drop") %>%
   mutate(b_bin = as.numeric(b_bin)/(length(my_breaks)-1)) %>%
  filter(is.finite(acc)) %>%
  ggplot(aes(b_bin, acc)) + 
  geom_point() + 
  geom_line(stat = "smooth", method = "loess", 
            formula = y ~ x, alpha = 0.65, size = 2, se = F) +
  geom_abline(linetype = 2) +
  scale_x_continuous("runner up item weights") +
  scale_y_continuous("proportion of times selected") + 
  coord_fixed()
```

@@

## Item Density
